### 2014-07-21 Neutral_simul.Rmd
Add compMethods_Time function

@@

@@

```{r simul_pomac467_T100,echo=F,message=F,warning=F}

@@

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Select a subset to test the procedure !
#
#den2 <- den2[den2$MortalityRate==.2 & den2$DispersalDistance==0.04 & den2$ColonizationRate==0.001, ]

mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- data.frame(time=100,notdif=propNotDiffSAD(mks100),method="SAD")

# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

@@

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

@@

rm(mks,psa,den1,den2,den3)

@@

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c3 <- c2
c3$method <- "SRS"

@@

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=100,notdif=propNotDiffSRS(c2),method="DqSAD"))

c2$method <- "DqSAD"
c3 <- rbind(c3,c2)

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

@@

kable(compM)

setwd(oldcd)
rm(c1,c2,Dq2)
rm(den1,den)
save.image()
```

# Simulations at T=500

```{r simul_pomac467_T500, eval=FALSE,echo=F,message=F,warning=F }

@@

# read par file with simulations parameters
if(simul)
{
  system("rm Exp467T100*")

@@

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 500
  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",nrow(ff),"T500")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

@@

  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  system(s)
}

# Read all simulations and change to long format

den1 <- meltDensityOut_NT(paste0(bName,"T500Density.txt"),spMeta)

# have to make averages of 
require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

names(den2)[6] <- "value" # the functions use this field name

# Test pairwise diferences in SAD
#
mks100 <- pairKS_SAD(den2)

# Which are not different
format(mks100[mks100$p.adjust>0.05,c(10:13,14:15)],digits=4)

# which is the proportion of not different
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSAD(mks100),method="SAD"))

# Plot the first pairs not different 
#
mks <- mks100[mks100$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

# Plot the first pair different 
#
mks <- mks100[mks100$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(value),colour=parms)) + geom_line())

rm(mks,psa,den1,den2,den3)

# Leer Dq SRS
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfOrd.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="SRS"))

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

c2$method <- "SRS"
c3 <- rbind(c3,c2)

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T500mfSAD.txt"))

#Dq1 <- with(Dq1,Dq1[MortalityRate==.2 & DispersalDistance==0.04 & ColonizationRate==0.001, ])

# Testing pairwise differences
#
c2 <- compDq_frame(Dq1,35)

# Build data.frame with proportion
#
compM <- rbind(compM, data.frame(time=500,notdif=propNotDiffSRS(c2),method="DqSAD"))

c2$method <- "DqSAD"
c3 <- rbind(c3,c2)

#c3 <- melt(Dq2, id.vars=c("factor","rep"), measure=c(3:37),variable="q",value.name="Dq")

plotDq_ReplaceR(Dq1,0.2,0.04,0.001)
plotDq_ReplaceR(Dq1,0.2,0.4,0.001)
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001)

kable(compM)

>>>>

# Load data if run only one chunk 
load(".RData")

@@

spMeta <- nrow(ff)

@@

```{r simul_pomac467_T100,echo=F,message=F,warning=F}
setwd("Simul")

@@

m <- compMethods_Time(bName,100,spMeta)

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SAD",]

# Which are not different
format(mks1[mks1$p.adjust>0.05,],digits=4)

den1 <- meltDensityOut_NT(paste0(bName,"T100Density.txt"),spMeta)
# Select a subset to test the procedure !
#
den1 <- den1[den1$MortalityRate==.2 & den1$DispersalDistance==0.04 & den1$ColonizationRate==0.001, ]

require(plyr)
den2 <- ddply(den1,.(MortalityRate,DispersalDistance,ColonizationRate,ReplacementRate,Species),summarise,den=mean(value))

# Plot the first pairs not different 
#

mks <- mks1[mks1$p.adjust>0.05,]
psa <- mergePairSAD(mks[1,],den2)

@@

(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line() + ggtitle("SAD not dif"))

# Plot the first pair different 
#
mks <- mks1[mks1$p.adjust<=0.05,]
psa <- mergePairSAD(mks[1,],den2)
(g <- ggplot(psa,aes(x=Rank,y=log(den),colour=parms)) + geom_line()
 + ggtitle("SAD different"))

@@

rm(mks,psa)

@@

@@

plotDq_ReplaceR(Dq1,0.2,0.04,0.0001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001, "SRS")
plotDq_ReplaceR(Dq1,0.2,0.04,0.001, "SRS")

mks1 <- m$mPval
mks1 <- mks1[mks1$method=="SRS",]

mks <- mks1[mks1$p.adjust<=0.05,]
# NO FUNCIONA MERGE
#psa <- mergePairSAD(mks[1,],Dq1)

#
#
# Leer Dq SAD
#
Dq1 <- readNeutral_calcDq(paste0(bName,"T100mfSAD.txt"))

plotDq_ReplaceR(Dq1,0.2,0.04,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.4,0.001,"DqSAD")
plotDq_ReplaceR(Dq1,0.2,0.04,0.0001,"DqSAD")

@@

compM

m$compM

compM <- m$compM

mPval <- m$mPval

setwd(oldcd)
rm(c1,c2,Dq2,Dq1)
rm(den1,den)
save.image()

## Simulations at Time=500

```{r simul_pomac467_T500, eval=T,echo=F,message=F,warning=F }

@@

# read par file with simulations parameters
if(simul)
{
  # Delete old simulations
  system("rm Exp467T500*")

@@

  # Number of time steps 
  par[par$V1=="nEvals",]$V2 <- 500
  par[par$V1=="inter",]$V2 <- 500 # interval to measure Density and Diversity
  par[par$V1=="init",]$V2 <- 500  # Firs time of measurement = interval
  par[par$V1=="modType",]$V2 <- 4 # Hierarchical saturated
  par[par$V1=="sa",]$V2 <- "N" # Save a snapshot of the model
  par[par$V1=="baseName",]$V2 <- paste0("Exp",spMeta,"T500")
  par[par$V1=="pomac",]$V2 <- 1 # 0:one set of parms 
                                # 1:several simulations with pomac.lin parameters

@@

  s <- paste(neuBin,"sim.par","fishE.inp")
  s
  system(s,wait=F)
}

m <- compMethods_Time(bName,500,spMeta)

compM <- rbind(compM,m$compM)

mPval <- rbind(mPval,m$mPval)
